\chapter{Background}
For the task of helmet detection, feature extraction from the dataset was a serious challenge. From our literature survey, we found that past works have used combinations of techniques like Local Binary Pattern, Histograms of Oriented Gradients and the Hough Transform descriptors\cite{b5} or other techniques like scale-invariant feature transform (SIFT), etc.\cite{b5}. Once we got all the relevant features from our dataset next step was to decide which classification techniques we should use. From our literature survey we found that past works have used techniques like K-Nearest Neighbour (KNN) classifier\cite{b6}, Support vector machine(SVM)classifier\cite{b6} or convolution neural network classifier(CNN)\cite{b8}.
\par The task of number plate detection is a well-known problem throughout the past decades. We had read two research papers on this problem. In the paper \cite{b3}, the authors have described an approach that consists of 4 steps. They are i) vertical edge image, ii) edge statistical analysis iii) hierarchical-based license plate location and iv) morphology-based license plate extraction. They have used connected component analysis to extract the foreground objects and then they have done feature extraction. Based on the collected features, they have filtered out the license plate with a very high accuracy rate. 
\par The paper \cite{b4} has followed a different approach. They have first done image preprocessing by converting the image into gray-scale and then denoised them. Then they have done the candidate area extraction by sliding window approach. Their final step was to do a character recognition to recognize the numbers present in the license plate. 
\par In our approach, we have used concepts from both the papers, i.e, we have done a connected component analysis to detect the objects from the image and then used morphological features of a number plate to filter out the number plates from several objects. After that, we have performed character recognition using machine learning to detect the characters present in the license plate.
