\chapter{Conclusion}

\par In this project, we have built three modules, i.e, Android application, helmet detection module and number plate detection module. \par The helmet detection module has achieved 75.7\% accuracy using transfer learning. The major bottleneck of this module was the small size of the dataset. There are a large variety of helmets present in our dataset. With a small dataset, it was difficult for our model to generalize. As part of our future work, we would enhance the dataset with more number of images, which would probably increase the accuracy.
\par The number plate detection module has achieved 75\%, 67.8\% and 63\% accuracy in number plate localization, character segmentation, and character recognition sub-module respectively using method 1. The method 2 has achieved 95.3\% accuracy rate in overall number plate detection given a video frame as input but it is taking nearly 1 minute to process only one video frame. The low accuracy rate in the first method is due to low-quality video frame and non-availability of enough amount of data for character recognition submodule.
\par The Android application's user interface can be made more attractive for real-time deployment. Also, new features such as incidents of talking on the phone while driving, accident detection can be implemented. To increase the accuracy of number plate detection module, neural networks can be used with large Indian number plate dataset.  

\par We believe that deployment of such an application would help in policing as well as bring down the number of road accidents.



