\cleardoublepage
%\pagebreak
\phantomsection
\addcontentsline{toc}{chapter}{References}
\begin{thebibliography}{99}

\bibitem{b0} OpenALPR Cloud API, \url{http://www.openalpr.com/cloud-api.html?country=in}.

\bibitem{b1} Connected component labeling - Wikipedia, \url{https://en.wikipedia.org/wiki/Connected-component_labeling#/media/File:Two-pass_connected_component_labeling.svg}.

\bibitem{b2} WHO | Global status report on road safety 2015, \url{http://www.who.int/violence_injury_prevention/road_safety_status/2015/en/}.

\bibitem{b3} B. Hongliang, L. Changping, ``A hybrid license plate extraction method based on edge statistics and morphology,'' Pattern Recognition, 2004. ICPR 2004. Proceedings of the 17th International Conference.

\bibitem{b4} H. Karwal, A. Girdhar, ``Vehicle Number Plate Detection System for Indian Vehicles,'' Computational Intelligence \& Communication Technology (CICT), 2015 IEEE International Conference.


\bibitem{b5} R. Silva and k.Aires and T. Santos, ``Automatic detection of motorcyclists without helmet,''Computing Conference (CLEI), 2013 XXXIX Latin American. 
\bibitem{b6} K. Dahiya and D. Singh and Mohan, C Krishna,``Automatic detection of bike-riders without helmet using surveillance videos in real-time",Neural Networks (IJCNN), 2016 IEEE International Joint Conference.
\bibitem{b7} R. Waranusast and N. Bundon and V. Timtong and C. Tangnoi,``Machine vision techniques for motorcycle safety helmet detection '', Image and Vision Computing New Zealand (IVCNZ), 2013 IEEE 28th International Conference.

\bibitem{b8}A. Krizhevsky, and I. Sutskever and Geoffrey E Hinton, ``Imagenet classification with deep convolutional neural networks,''Advances in neural information processing systems, 2012.

\bibitem{b9} Draknet for object detection, \url{https://pjreddie.com/darknet/}.

\bibitem{b10} Image classification using keras, \url{https://blog.keras.io/building-powerful-image-classification-models-using-very-little-data.html}.

\bibitem{b11} android.hardware.camera2 | Android Developers, \url{https://developer.android.com/reference/android/hardware/camera2/package-summary.html}.

\bibitem{b12}Tesseract OCR, \url{https://opensource.google.com/projects/tesseract}.

\bibitem{b13} R. Bhandari, B. Raman, V. Padmanabhan, ``FullStop: Tracking unsafe stopping behaviour of buses,'' Communication Systems and Networks (COMSNETS), 2018 10th International Conference.

\bibitem{b14} skimage -- skimage v0.14dev docs\url{http://scikit-image.org/docs/dev/api/skimage.html}.

\end{thebibliography}
